Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-09-02 summary.tex
now

\label{sec:overview}
Our method is designed for boolean operations on arbitrary number of triangle meshes. Input mesh primitives are required to be watertight and not self-intersected, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}. Despite of so many constraints, our method is not sensitive to topology deficiencies and works well if deficiencies are not near the intersection areas between meshes.

@@

\begin{itemize}[leftmargin=0.45cm]
\item[1)] The basic routine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of the supporting plane (denoted as $p(t_1)\colon(a, b, c, d)$) of a face with respect to a certain vertex (denoted as  $v_i(t_2)\colon(x, y, z)$) of the other face. That is to compute:
\begin{equation}\label{eq:plane}
sign(ax+by+cz+d).
\end{equation}
Reviewing the discussion of section \ref{sec:convert},  the coordinates of vertices are represented by three L-bit float point numbers.Precisions of the four coefficients of the supporting plane are $(P^\star, P^\star, P^\star, P)$. Here $P$ is defined in equation \ref{eq:precision}, and $$P^\star=P-(L-1)-2.$$ Using the enforced criterion $M \ge P+1$, we find that $M$ bits are enough to perform the predicate of equation \ref{eq:plane}. This allow us to perform the early discard efficiently.
\item[2)]In step 2, the end points of $Seg_1$ and $Seg_2$ are implicitly represented using intersections of plane triples. Take $Seg_1$ as an example. As illustrated in Fig. \ref{fig:isect}, $Seg_1$ are the intersection between $t_1$ and $p_s(t_2)$. Because the edge $e_i(t_1)$ can be represented as $(p^s( t_1), p^b_i(t_1))$, the end points of $Seg_1$ can be represented in the form of $(p^s( t_1), p^s(t_2), p^b_i(t_1))$. In Fig. \ref{fig:isect}, we list all intersection situations between $t_1$ and $p_s(t_2)$, and the corresponding bounding plane $p^b_i(t_1)$ in each situation. Coplanar conditions will be discussed later in section \ref{sec:degenerate}.
 \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $l$ (Fig. \ref{fig_projection}), where $l$ is the intersection between $p_s(t_1)$ and $p_s(t_2)$. Because end points are all represented using plane triples, we can use the two-line-one-plane comparison discussed in section \ref{sec:substrates} to perform the comparison.
\end{itemize}

@@

Intersection refinement is performed in a local scope. For each face, we detect irregular intersections by intersection test between pairs of intersections. Because primitive meshes are not self-intersected, we only check intersections between intersections made by different meshes. Face intersecting only one other mesh do not need refinement, since they do not have such intersection pairs.

>>>>

\label{sec:overview}
Our method is designed for boolean operations on arbitrary number of triangle meshes. Input mesh primitives are required to be watertight and not self-intersecting, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}. Despite of so many constraints, our method is not sensitive to topology deficiencies and works well if deficiencies are not near the intersection areas between meshes.

@@

\begin{itemize}[leftmargin=0.45cm]
\item[1)] The basic routine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of the supporting plane (denoted as $p(t_1)\colon(a, b, c, d)$) of a face with respect to a certain vertex (denoted as  $v_i(t_2)\colon(x, y, z)$) of the other face. That is to compute:
\begin{equation}\label{eq:plane}
sign(ax+by+cz+d).
\end{equation}
Reviewing the discussion of section \ref{sec:convert},  the coordinates of vertices are represented by three L-bit float point numbers.Precisions of the four coefficients of the supporting plane are $(P^\star, P^\star, P^\star, P)$. Here $P$ is defined in equation \ref{eq:precision}, and $$P^\star=P-(L-1)-2.$$ Using the enforced criterion $M \ge P+1$, we find that $M$ bits are enough to perform the predicate of equation \ref{eq:plane}. This allow us to perform the early discard efficiently.
\item[2)]In step 2, the end points of $Seg_1$ and $Seg_2$ are implicitly represented using intersections of plane triples. Take $Seg_1$ as an example. As illustrated in Fig. \ref{fig:isect}, $Seg_1$ are the intersection between $t_1$ and $p_s(t_2)$. Because the edge $e_i(t_1)$ can be represented as $(p^s( t_1), p^b_i(t_1))$, the end points of $Seg_1$ can be represented in the form of $(p^s( t_1), p^s(t_2), p^b_i(t_1))$. In Fig. \ref{fig:isect}, we list all intersection situations between $t_1$ and $p_s(t_2)$, and the corresponding bounding plane $p^b_i(t_1)$ in each situation. The conditions that $t_1$ is inside the plane $p_s(t_2)$ (coplanar cases) will be discussed later in section \ref{sec:degenerate}.
 \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $l$ (Fig. \ref{fig_projection}), where $l$ is the intersection between $p_s(t_1)$ and $p_s(t_2)$. Because end points are all represented using plane triples, we can use the two-line-one-plane comparison discussed in section \ref{sec:substrates} to perform the comparison.
\end{itemize}

@@

Intersection refinement is performed in a local scope. For each face, we detect irregular intersections by intersection test between pairs of intersections. Because primitive meshes are not self-intersecting, we only check intersections between intersections made by different meshes. Face intersecting only one other mesh do not need refinement, since they do not have such intersection pairs.
